\documentclass{article}
\title{Van}
\author{By Santi, anon}
\date{9/14/21}

\begin{document}
\maketitle

	This is mainly a more calm and collected collection of Van’s wrongdoings to possibly 9+ people.

	BIG TRIGGER WARNING: RAPE, SEXUAL ASSAULT, MENTAL ABUSE.
DO NOT SEND DEATH THREATS OR HURT HIM, HIS FAMILY DID NOTHING WRONG, DO NOT HURT ANYONE OVER THIS SITUATION.
	I won’t be holding back on saying what he did but no names but mine will be said.

\section{Me, scroll down to see the main acts he did}

\hspace{\parindent}First of all, let’s start with the tamer things on the list, “taps”. I can pretty
positively say I was the first victim to him for a lot of things, emotional, sexual, and
mental abuse starting with punching me in my private area nearly every day I saw him
multiple times a day starting in 7th grade. This act has been seen with several other
people even with people that he didn’t pursue sexually assaulting. The mental abuse he
did to me seems stupid but to me, a kid that still has a lot of trouble socializing in a
place that I’m still trying to understand the social environment as an immigrant.

	The mental abuse he did to me was very lasting, I would say it has easily had the
longest-lasting impact on me because it was petty as fuck. We had an argument over
Rainbow 6 Siege, a high-intensity, close-quarters first-person shooter that he prided on
being the best in the group, even though he was realistically the only person taking it
seriously. The one situation that set him off and got him to cut me off was because I was
under so much pressure I “didn’t know” the difference between left and right. He
blocked me, wouldn't talk to me at school and sat next to me every day at lunch. 

	After we reconciled that we had another similar fight during Christmas break and that’s
where I had my first big break, I got really emotional and depressed where I pretty much
just stopped making friends in person. I would be good friends with people online, some
people that I made friends with online from a video game, and some that I barely saw in
school. I blame him for my lack of social skills now, he broke me socially, after we
reconciled again like a year later in high school he had the fucking audacity to say that
he changed and he was a better person but instead of that all he was doing is masking
that he’s still the same manipulative person.

	I don’t want to call myself the most broken victim from this whole situation of 3 years
of sexually assaulting others, but looking at it now, it took me years to even start
recovering. The others have really good safety nets while I realize how little I care for
myself. I got myself in a relationship where I knew it was going to end because of my
overall schedule. Combining that with the mental abuse Van was doing to me every day
almost broke me socially again but this time I had a backup which was just another friend
group.

	In the end, all I have to say is… at least I made it out of there with the amount
of sanity and emotional stability I still have.

\section{His more serious acts on others - }

\hspace{\parindent}I can’t say that these acts have directly affected me since he did not rape, sexually
assault me, or mentally abuse me to these extents. But to start off with the most
detailed situation we have, on a certain sleepover during the summer of 2021, Van while
mostly everyone and the victim were asleep, Van pulled up the pants of this victim, took
pictures, and jacked them off while the victim was not fully asleep but so in shock that
they could not act, for 3 fucking hours. To add to the disgust that everyone has of the
situation, he then texted the victim’s significant other about how the victim was excited
during his sleep and was thinking of them(S/O) and how big they were. This was the
situation that set off the first separation of the group. Van took a hiatus saying it was
for his “mental health” using his very recent breakup(literally 1-week relationship) as
evidence to sort of support that, though we found later that he was traveling to Florida
and New Orleans. This hiatus was simply to dodge the instant consequences of his actions
on this victim.

	These situations have less info on them since these more serious acts were when the
victims were asleep or almost asleep. One situation was where Van straight-up jerked
someone off while they were “asleep” but like the previous situation, the victim was so
in shock that they couldn’t act to stop Van. Another less successful situation was when
Van tried to take the pants off of another potential rape victim but this time the victim
was fully awake and stopped Van. I might have had a similar situation to these because
one time at a sleepover he mentioned how I had a boner when I was dead asleep and maybe
on other sleepovers he might have acted on me while I was dead asleep but I guess I’ll
never know. 

	This next situation is a very heavy story of his mental abuse and manipulation. Van is a
very egotistical and narcissistic person, always claiming he is a good person, pretty
much having a hero complex around the group not really thinking that a lot of people just
have conflicting ideas and personalities. This contributed so much to this heavy mental
abuse situation because this person was so badly affected that they had to be sent to a
mental hospital which really only made it worse. Van played victim throughout the
situation yet used others to dig info about this victim then sending him to a worse
facility. This made this victim very depressed and at a point suicidal but even though
they are barely an acquaintance I’m very glad they’re still here and are able to tell
their story about this monster.

	This last, less in detail situation is about similar "taps" (touching in their
private area) but to someone whose sister had just committed suicide.

	Side note: as many remember there was a similar situation of CP that Van got ALC for
during 7th grade but this victim hasn’t come out or reached out `after the first roll-out
of exposing.

	Thank you for reading this and if you would like to spread the word of Van’s actions
please use this doc. This is the most detailed possible account of all his actions, best
of luck to all.

	- santi


\section{Red Flags}
\hspace{\parindent}All written below is from an anonymous person but not me.


	I decided that I would share the red flags that I chose to ignore. I still feel at fault
for not noticing them enough and putting it off as him just being a guy. However I had
just come out of a toxic and abusive relationship, and didn’t know was right from wrong. 

	He would randomly print out pictures of his friends and keep them with him. It was his
prized possessions, and he loved having attractive friends. He used to show me pictures
of my current boyfriend before we were together. He would talk about his body and how hot
he was. He would remind me that he was out of my league and told me that nobody deserved
a chance with him. He would constantly sexualize him and his other friends.

	He would constantly threaten to hurt me if I did something wrong, which I put off as
normal because I was convinced that men act this way and this is the way I would be
treated for being female. He would cuss me out and belittle me and make me feel like an
idiot. He would constantly say he didn’t care about me and call me a bitch when I purely
wanted to be his friend.

	He was too comfortable talking about his penis and would ask guys in the many chats I had
been in what everyone's size was. I stated to him that this made me very uncomfortable
and he still did it.

	He was too engrossed in my relationship with my boyfriend. He would want to know every
step of our relationship, and every date we had been on when it was purely none of his
business. I remember he got mad at my boyfriend and I when we didn’t immediately tell him
we went on our first date. And when we were finally going out he wanted the two of us one
on one to go to his house for a date so he could make us food and observe us.

	He would get mad when someone cared for him and would shut off. While this is normal, he
would be blatantly rude about it. After he was rude he always found ways to make himself
the victim

	He would make jokes about my suicide attempts, and constantly told me they were stupid
and he would get a good laugh about me struggling. If I was not in a position where I
felt like being honest about my mental health, I would say “I’m typically a happy
person!” he would make it obvious that i wasn’t and get a good laugh out of mentioning my
depression and suicide attemps

	The day after he assaulted my boyfriend when he thought he was asleep, he texted me
commenting on my boyfriend's penis. Here is a list of the things he said to me

\begin{itemize}
	\item He was definitely dreaming about you
	\item He was hard as fuck
	\item He was huge
	\item His penis was so sweaty
	\item He must want to have sex with you
	\item You are lucky he feels this way about you
\end{itemize}

	I only started to realize something was up with the last red flag. This is a reminder to
never dismiss odd and creepy behavior. Trust the people who tell you someone is a bad
person, and never let someone belittle you and make you feel like shit. You are never
overreacting, and you are never being dramatic.


\end{document}

